### 2018-06-21 Writeup/PERT_New.tex
Add the mixed process and colGen process

@@

	Problem~\eqref{prob2:extensive} is a two-stage stochastic mixed integer program with binary variables in the second stage.

>>>>

	\textcolor{blue}{Add the two activity closed form solution test. Add the conclusion of consistency. Add the proof of consistency. Prove the inconsistency of the stratified sampling method. }
	Model~\eqref{prob2:extensive} is a two-stage stochastic mixed integer program with binary variables in the second stage. It is a type of hard problem that efficient decomposition methods have only been found when additional properties about variables exist \textcolor{blue}{cite past literatures with second stage integers.}

@@
